---
title: "DaSPPA product graphs"
subtitle: "This document will generate the requisite graphs and data analysis"
date: "2023-12-01"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, echo = FALSE, warning = FALSE)
```


```{r, echo=TRUE}
library(tidyverse) 
library(reshape2)
library(dplyr)
library(ggrepel)
library(datawizard)
library(knitr) 
library(kableExtra)  
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(stringi)
library(mapproj)
library(factoextra)
library(cluster)
library(klaR)
library(maps)
library(passport)
library(tidytext)
library(textdata)

set.seed(25536)
```

### Data Preprocessing
```{r}
unvotes <- read.csv("data/dataverse_files/UNVotes.csv")
idealpointestimates <- read.csv("data/dataverse_files/IdealpointestimatesAll_Jul2023.csv")

#unvotes$date <- as.Date(unvotes$date)

un_vote_data <- unvotes |>
  dplyr::mutate(date = as.Date(date, format="%Y-%m-%d")) |> 
  dplyr::select(Country, date, resid, vote, importantvote, me, nu, di, hr, co, ec) |>
  dplyr::filter(date >= as.Date("2000-01-01", format="%Y-%m-%d"))



```


#### Pre-Training analysis
Using Elbow method and gap statistic, we aim to find the optimal cluster gap. 

There are elbows at 3 and 5. Gap statistic analysis shows 8 is optimal, but 5 is a local turning point as well. Thus, we can use 5.
```{r}
#optional: eval=FALSE
gc()

df <- un_vote_data |> filter(importantvote == 1)
dfm <-na.omit(df)

data <- dfm |> dplyr::select(Country, resid, vote)
data_transposed <- data %>%
  spread(key = resid, value = vote)

dfm <-na.omit(data_transposed)
dfm2 <- dfm[, -1]

fviz_nbclust(dfm2, kmeans, method = "wss") +
      geom_vline(xintercept = 3, linetype = 2)+
      labs(subtitle = "Elbow method")

gc()

gap_stat <- clusGap(dfm2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
fviz_gap_stat(gap_stat)
gc()
```
Why 5 clusters? 5 UNSC superpowers.

#### Fitting the k means model.
```{r}
k <- 5

gc()

df <- un_vote_data |> filter(importantvote == 1)
dfm <-na.omit(df)

data <- dfm |> dplyr::select(Country, resid, vote)
data_transposed <- data %>%
  spread(key = resid, value = vote)

dfm <-na.omit(data_transposed)
dfm2 <- dfm[, -1]


km.res <- kmeans(dfm2, centers = k, nstart = 1000) 
fviz_cluster(km.res, data=dfm2)

km.res <- kmeans(dfm2, centers = k, nstart = 1000) 
fviz_cluster(km.res, data=dfm2)

sf::sf_use_s2(FALSE) 

#km.res['Country']=labels
world2E <- ne_countries(scale="medium", returnclass = "sf")
#world2E <- st_make_valid(world2E)
#world2E <- st_simplify(world2E, dTolerance = 100)
#wrd <- world2E |> dplyr::mutate(Country = as_country_code(geounit, from="en",to = "iso3c"))

wrd <- world2E |> 
  dplyr::mutate(Country = iso_a3)

```

```{r}

dfm['cluster']= km.res$cluster


wrdonly <- anti_join(wrd, dfm, by = "Country")
summary_1 <- wrdonly |> 
  dplyr::group_by(Country) |> 
  dplyr::summarize(count = n()) 

unvotesonly <- anti_join(dfm, wrd, by = "Country")
summary_2 <- unvotesonly |> 
  dplyr::group_by(Country) |> 
  dplyr::summarize(count= n()) 

summary_1
summary_2

country_group <- dfm |> dplyr::select(Country, cluster)


combined <- right_join(country_group, wrd, by = "Country")


combined |> ggplot(aes(fill=cluster)) +
  geom_sf(aes(geometry=geometry)) +
  coord_sf() +
  labs(x=NULL, y=NULL, fill="UN Vote Alliance Clustering using K-Means") +
  guides(x = "none", y = "none") 

```


### Part 2: Graph Network Analysis



### Part 3: Sentiment Analysis and Regression.
```{r}
presscon <- readxl::read_xlsx("data/Sentiment/CMFA_PressCon_v3.xlsx")

press_select <- presscon |> dplyr::select(question_lem, answer_lem, q_loc, a_loc)

```




```{r}
# Assuming your dataframe is named 'df' and has columns A and B
# Load a sentiment lexicon (e.g., AFINN) for sentiment analysis
afinn <- get_sentiments("afinn")

# Function to calculate sentiment for a row
calculate_row_sentiment <- function(row) {
  sentiment_question <- row %>%
    dplyr::select(question_lem) %>%
    unnest_tokens(word, question_lem) %>%
    inner_join(afinn) %>%
    summarize(sentiment_question = sum(value))

  sentiment_answer <- row %>%
    dplyr::select(answer_lem) %>%
    unnest_tokens(word, answer_lem) %>%
    inner_join(afinn) %>%
    summarize(sentiment_answer = sum(value))

  overall_sentiment <- case_when(
    sentiment_question$sentiment_question >= 0 ~ sentiment_answer$sentiment_answer,
    sentiment_question$sentiment_question < 0 ~ sentiment_answer$sentiment_answer
  )

  return(cbind(row, sentiment_question, sentiment_answer, overall_sentiment))
}

# Apply the function row-wise to the dataframe
sentiment_speech <- press_select %>%
  group_by(row_number()) %>%
  do(calculate_row_sentiment(.))
```


```{r}
# TODO: Process countries mentioned: if countries appear in A and B locations




# TODO: Now, convert positive/negative into a scale of -1,0,1.




```


```{r}
# TODO: Calculate absolute distance between pairs of countries.
# Using idealpointestimates, use IdealPointAll to calculate the ideal point difference (absolute value) for every pair of countries.


# TODO: Use logistic regression, map 


```









### Part 2: Graph Network Analysis


### Part 3: Regression and Sentiment Analysis

We carry out sentiment analysis on the statements of Q&As of Chinese Ministry of Foreign affairs 










